---
title: "GLMhw-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{GLMhw-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(GLMhw)
```

# Introduction

The R package `GLMhw` is used to build a logistic regression model and use the Newton algorithm for parameter estimation. The package implements model training (`my_logistic_regression.formula`), prediction (`predict.my_logistic_regression`), drawing ROC curves (`plot_roc`), and printing models (`print.my_logistic_regression`). The S3 method is used in the function definition.

# Example
## Build a logistic regression model
```{r}
data(test_data)
model <- my_logistic_regression(y~x1+x2, data=test_data)
# print model
print(model)
```

## Prediction
```{r}
pred <- predict(model,test_data[1:10,])
pred
```

## Draw ROC curve

```{r}
plot_roc(model)
```

## Compute accuracy
```{r}
accuracy(pred$prob,test_data$y[1:10])
```

# Correctness

The logistic regression results of the `glm` function and this R package are consistent.
```{r}
model_true <- glm(y~x1+x2,data=test_data, family=binomial)
summary(model_true)
```

The estimated coefficients are consistent.
```{r}
coef_true <- round(as.vector(coef(model_true)),5)
coef_cur <- round(as.vector(t(coef(model))),5)
all.equal(coef_true,coef_cur)
```


# Performance
```{r}
bench::mark(
  min_time = .1,
  {model_true <- glm(y~x1+x2,data=test_data, family=binomial)
  round(as.vector(coef(model_true)),5)
  },
  {model <- my_logistic_regression(y~x1+x2, data=test_data)
  round(as.vector(t(coef(model))),5)
  }
)
```